Object Naming in Language and Vision: A Survey and a New Dataset

### 2019-11-29 papers/LREC2020/analysis.tex

We analyze the response sets obtained per object, that is, the set of names and their frequency (number of annotators entering a particular name).
Our analysis of naming variation shows that, on the one hand, we have a fair bit of consistency in the names chosen for objects, and, on the other, also consistent variation.
Figure \ref{fig:ntypes} shows the cumulative histograms for type counts, i.e.\ how many objects have at least $n$\ names, with different frequency thresholds~$t$.
Without any frequency thresholding~\mbox{($t$=1}, that is, allowing names entered by only one annotator)}, the proportion of instances that have a single name annotated is very small, below\ $10\%$, and there is a long tail of datapoints with many names, up to 19. 
With a reasonable (based on data inspection; names entered by one annotator only have the most noise, which is to be expected) threshold of $t$=2, a bit over $20\%$\ of the objects have one name, almost $50\%$\ up to $3$\ names, and $100\%$\ up to $8$\ names.
This threshold is the one illustrated in Fig.~\ref{fig:ex-high-low-agreement}, which includes names that have at least frequency 2.
The average number of names with this threshold is\ $2.9$, and the most frequent name accounts on average for $75\%$\ of the responses for a given object (Table~\ref{tab:agree}, and see below).
Thus, in our data objects tend to have a preferred name, as expected from work in Psychology \cite{rosch1976basic,jolicoeur1984pictures}, and at the same time there is variation.

>>>>

We analyze the response sets obtained per object, that is, the set of names and their frequency (number of annotators entering a particular name).
Our analysis of naming variation shows that, on the one hand, we have a fair bit of consistency in the names chosen for objects, and, on the other, also consistent variation.
Figure \ref{fig:ntypes} shows the cumulative histograms for type counts, i.e.\ how many objects have at least $n$\ names, with different frequency thresholds~$t$.
Without any frequency thresholding~\mbox{$t$=1}, that is, allowing names entered by only one annotator, the proportion of instances that have a single name annotated is very small, below\ $10\%$, and there is a long tail of datapoints with many names, up to 19. 
With a reasonable (based on data inspection; names entered by one annotator only have the most noise, which is to be expected) threshold of $t$=2, a bit over $20\%$\ of the objects have one name, almost $50\%$\ up to $3$\ names, and $100\%$\ up to $8$\ names.
This threshold is the one illustrated in Fig.~\ref{fig:ex-high-low-agreement}, which includes names that have at least frequency 2.
The average number of names with this threshold is\ $2.9$, and the most frequent name accounts on average for $75\%$\ of the responses for a given object (Table~\ref{tab:agree}, and see below).
Thus, in our data objects tend to have a preferred name, as expected from work in Psychology \cite{rosch1976basic,jolicoeur1984pictures}, and at the same time there is variation.

### 2019-11-29 papers/LREC2020/data-collection.tex

We take data from \vgenome~(VG, \newcite{krishna2016visualgenome}), which
contains a dense region-based labeling of $108$K~images with, inter alia, object names, attributes and relationships,
all linked to WordNet synsets \cite{fellbaum1998wordnet}.
\vg suits our purpose of collecting names for naturalistic instances of common objects, as it has images of varying complexity, with close-ups as well as images with many objects.
As common in Computer Vision, objects are localized as bounding boxes, as in Figure~\ref{fig:cake}.% 
\footnote{We use image and object interchangeably in the following, since we only selected one target object per image (i.e., each object and image in VG is chosen at most once).}

@@

First, to create our synset set, we chose those \vg synsets that match or subsume the object classes in the McRae norms, and have a high number of \vg object instances of different names.\cs{prev. sentence this is still a bit fluffy}
For example, \vg instances subsumed by McRae's \textsl{dog} were named \textsl{beagle, greyhound, puppy, bulldog}, etc., while McRae's \textsl{duck}, \textsl{goose}, or \textsl{gull} did not have name variants in \vg, so we kept \textsl{dog} and \textsl{bird} (which subsumes \textsl{duck}, \textsl{goose}, or \textsl{gull}) as collection synsets.
%\gbt{Just to clarify: we also collected objects named \textsl{duck}, \textsl{goose}, or \textsl{gull}, right? Not only \textsl{bird}?}

We then retrieved all VG images depicting an object whose name matches or is subsumed by words in one of these synsets; we refer to these words as \textit{seeds} ($450$\ in total).
\gbt{from the dataframe in the github it's 449. Also, there are some mistakes in the list of seeds ('dugout.', 'man's') -- to check after the deadline.}
We did not consider objects with names in plural form, with parts-of-speech other than nouns\footnote{We obtained tags with CoreNLP \cite{manning2014stanford}.}, or that were multi-word expressions (e.g.,~\textsl{pink bird}). 
We further only considered objects whose bounding box covered~\mbox{$20-90\%$} of the image area.
% We based the definition of our set of nodes on the WN (REF) synsets of the McRae concepts (e.g.,~dog, duck, goose, gull), the nominal WordNet hierarchy, and the frequency distribution of the VG object names' synsets.\footnote{TODO: need to be clear from the general description of VG that the frequ. of instances labeled with the synset of the object name is meant.} 
% First, we selected a set of collection node candidates---synsets which match (e.g.,~\textsl{dog, duck, goose, gull}) or subsume (e.g.,~\textsl{mammal, bird}) the McRae synsets\footnote{Specific synset IDs, e.g.,~dog.n.01, are omitted for readability.}. 
% From these candidates we kept those as collection nodes which had a high frequency of VG object instances of different names. For example, VG instances  subsumed by McRae's \textsl{dog} were named \textsl{beagle, greyhound, puppy, bulldog}, etc., while McRae's \textsl{duck, goose}, or \textsl{gull} did not have name variants in VG, so we kept \textsl{dog} and \textsl{bird} as collection nodes.
%\paragraph{Collection of instance candidates}
% Goal of above procedure was the collection of instances of selected object classes---our nodes--- whose VG names correspond to or subsume (are hypernyms of) a McRae concept, and whose object names differ, that is, of which we can expect that people possess different names for them (e.g.,~\textsl{duck, goose, gull} for \textsl{bird}).
% \paragraph{Sampling of instances}
Because of the Zipfian distribution of names, and to balance the collection, we sampled instances depending on the size of the seeds: up to $500$\ instances for seeds with up to $800$\ objects, and up to $1000$\ instances for larger seeds. This yielded a dataset of\ $31,093$~instances, which was further pruned during annotation, as explained next.
Table~\ref{tab:overview_dataset1} shows the top 5 \vg names in each of the domains.

>>>>

We take data from \vgenome~(VG) because its dense annotations of images can be beneficial to analyze the factors affecting naming (e.g.,\ the category or salience of other objects), and how these impact the modeling of natural language in L\&V.
\vg suits our purpose of collecting names for naturalistic instances of common objects, as it has images of varying complexity, with close-ups as well as images with many objects.
Moreover, its object names are linked to WordNet synsets \cite{fellbaum1998wordnet}, which affords analysis possibilities that we will exploit in Section~\ref{sec:analysis} below.
% The object names were obtained from the region descriptions (see Section~\ref{sec:vg-survey}).
Note that, as common in Computer Vision, objects in \vg images are localized as bounding boxes, as shown in Figure~\ref{fig:cake} (left).% 
\footnote{We use image and object interchangeably in the following, since we only selected one target object per image (i.e., each object and image in VG is chosen at most once).}

@@

First, to create our synset set, we chose those \vg synsets that match or subsume the object classes in the McRae norms, and cover different names in \vg.
%which \vg objects get diverse names.
For example, \vg instances subsumed by McRae's \textsl{dog} were named \textsl{dog, beagle, greyhound, puppy, bulldog}, etc., while McRae's \textsl{duck}, \textsl{goose}, or \textsl{gull} did not have name variants in \vg, so we kept \textsl{dog} and \textsl{bird} (which subsumes \textsl{duck}, \textsl{goose}, or \textsl{gull}) as collection synsets.
%\gbt{Just to clarify: we also collected objects named \textsl{duck}, \textsl{goose}, or \textsl{gull}, right? Not only \textsl{bird}?}

We then retrieved all VG images depicting an object whose name matches a word in these collection synsets or in those subsumed by them. We refer to the names obtained as \textit{seeds} ($450$\ in total).
%\gbt{from the dataframe in the github it's 449. Also, there are some mistakes in the list of seeds ('dugout.', 'man's') -- to check after the deadline.}
We did not consider objects with names in plural form, with parts-of-speech other than nouns\footnote{We obtained tags with CoreNLP \cite{manning2014stanford}.}, or that were multi-word expressions (e.g.,~\textsl{pink bird}). 
We further only considered objects whose bounding box covered~\mbox{$20-90\%$} of the image area.
% We based the definition of our set of nodes on the WN (REF) synsets of the McRae concepts (e.g.,~dog, duck, goose, gull), the nominal WordNet hierarchy, and the frequency distribution of the VG object names' synsets.\footnote{TODO: need to be clear from the general description of VG that the frequ. of instances labeled with the synset of the object name is meant.} 
% First, we selected a set of collection node candidates---synsets which match (e.g.,~\textsl{dog, duck, goose, gull}) or subsume (e.g.,~\textsl{mammal, bird}) the McRae synsets\footnote{Specific synset IDs, e.g.,~dog.n.01, are omitted for readability.}. 
% From these candidates we kept those as collection nodes which had a high frequency of VG object instances of different names. For example, VG instances  subsumed by McRae's \textsl{dog} were named \textsl{beagle, greyhound, puppy, bulldog}, etc., while McRae's \textsl{duck, goose}, or \textsl{gull} did not have name variants in VG, so we kept \textsl{dog} and \textsl{bird} as collection nodes.
%\paragraph{Collection of instance candidates}
% Goal of above procedure was the collection of instances of selected object classes---our nodes--- whose VG names correspond to or subsume (are hypernyms of) a McRae concept, and whose object names differ, that is, of which we can expect that people possess different names for them (e.g.,~\textsl{duck, goose, gull} for \textsl{bird}).
% \paragraph{Sampling of instances}
Because of the Zipfian distribution of names, and to balance the collection, we sampled instances depending on the size of the seeds: up to $500$\ instances for seeds with up to $800$\ objects, and up to $1000$\ instances for larger seeds. This yielded a dataset of\ $31,093$~instances, which was further pruned during annotation, as explained next.
Table~\ref{tab:overview_dataset1} shows the top 5 \vg names in each of the domains. \gbt{If someone feels like it: It'd be good to use small caps for domains throughout, and also to have the same (alphabetical?) order for all domains in all tables.}

### 2019-11-29 papers/LREC2020/survey.tex

%\cs{If space allows, I would also put an example image+annotation for RefCOCO and Flickr30kE}
%\gbt{Space doesn't seem to allow :)}
We identified three previously existing resources that can be of use for analysis and modeling of object naming: RefCOCO (and a variant, RefCOCO+), Flickr30k Entities, and Visual Genome. %
Table~\ref{tab:compare} summarizes their main characteristics and compares them to our dataset (last two columns; see Section~\ref{sec:data}).
As the table shows, previous datasets provide between one and three annotations per object, which, we believe, is not enough to assess naming behavior for individual objects and which
motivates our data collection. %, in which we collect 36 names per object.
In the following, we will look at their characteristics in more detail and work out requirements for a dataset that is suitable below for a large-scale, in-depth study targeted at object naming.

@@

One of the main advantages of \vg are its size, with 3.8 million objects as opposed to 50K and 243K for the other two datasets, and its category coverage, with a vocabulary of object names of 105K compared to 5K/10K.
Another is the fact that it, in principle, provides exhaustive annotations of objects in the image, often with several region descriptions and possibly object names per object.
This should make it easier to identify factors intervening in naming choices, and to model contextual aspects that may affect them, than in the case of \refcoco.

However, there is a crucial pitfall: As Figure \ref{fig:bird} shows, there is only a partial linking of objects that are mentioned across different region descriptions; for instance, the first, second, and fifth object IDs in the figure actually correspond to the same object.
Moreover, the regions for the beak of the object (third and fourth object IDs) overlap with those of the bird.
This means that the identity of objects cannot be established based on the annotation, which severely limits the usefulness of the data to analyze naming.
The relatively low number of annotations per objects in VisualGenome (1.7 on average) shown in Table \ref{tab:compare} and the very small number of objects that have more than one name associated with it (5\%) seem to be an effect of this problem.
Thus, even though there is a different name (\textit{vulture}) for \textit{bird} object in Figure \ref{fig:bird}, this cannot be established based on the given data.
We experimented with filtering and merging bounding boxes based on overlap, but this would introduce substantial noise into the data (e.g.\ truly overlapping objects).

Table \ref{tab:compare} also shows the statistics for the subset of objects that we selected for ManyNames and, here, we find a considerably higher average of annotations per object (7). However, interestingly, the portion of objects that have different names associated with them is still extremely small.
Note that, even though RefCOCO has much less annotations per object, there are many objects with different names (70\%).

@@

\subsection{Discussion}
\cs{@Sina I changed some stuff here, maybe you prefer the old version...}
As the discussion above showed, while some existing resources can be used to shed light on factors affecting naming choices, they do not provide enough data to systematically assess how variable object naming really is. The RefCOCO data suggest that many objects  object-specific naming behavior: To what extent do different people choose the same name for a specific object? How much variation is there? 
To answer these sorts of questions, we need naming data from many subjects for the same objects. 
Also, dense annotations of images can be beneficial to analyze the factors affecting naming (e.g.,\ the category or salience of other objects), and how these impact the modeling of natural language in L\&V.
These are the motivations for our dataset, ManyNames, and for building it on top of \vg, as discussed next.

>>>>

%\cs{If space allows, I would also put an example image+annotation for RefCOCO and Flickr30kE}
%\gbt{Space doesn't seem to allow :)}
We identified three previously existing resources that can be of use for analysis and modeling of object naming: RefCOCO (and a variant, RefCOCO+), Flickr30k Entities, and Visual Genome. %
Table~\ref{tab:compare} summarizes their main characteristics and compares them to our dataset (last two columns; see Section~\ref{sec:data}).
As the table shows, previous datasets provide between one and three annotations per object, which, we believe, is not enough to assess naming behavior for individual objects and which
motivates our data collection. %, in which we collect 36 names per object.
In the following, we will look at their characteristics in more detail and work out requirements for a dataset that is suitable for a large-scale study of object naming.

@@

One of the main advantages of \vg are its size, with 3.8 million objects ($108$K images) as opposed to 50K and 243K for the other two datasets, and its category coverage, with a vocabulary of object names of 105K compared to 5K/10K.
Another is the fact that it in principle provides exhaustive annotations of objects in the image, often with several region descriptions and possibly object names per object.
This should make it easier to identify factors intervening in naming choices, and to model contextual aspects that may affect them, than in the case of \refcoco.

However, there is a crucial pitfall: As Figure \ref{fig:bird} shows, there is only a partial linking of objects that are mentioned across different region descriptions; for instance, the first, second, and fifth object IDs in the figure actually correspond to the same object.
Moreover, the regions for the beak of the object (third and fourth object IDs) overlap with those of the bird.
This means that the identity of objects cannot be established based on the annotation, which severely limits the usefulness of the data to analyze naming.
For instance, even though there is a different name (\textit{vulture}) for \textit{bird} object in Figure \ref{fig:bird}, the annotation suggests that \textit{bird} is the only available name. 
The relatively low number of annotations per objects in VisualGenome (1.7 on average) shown in Table \ref{tab:compare} and the very small number of objects that have more than one name associated with it (5\%) seem to be an effect of this partial linking problem.
We experimented with filtering and merging bounding boxes based on overlap, but this would introduce substantial noise into the data (e.g.\ truly overlapping objects).

Table \ref{tab:compare} also shows the statistics for the subset of those VG objects that we selected for ManyNames and, here, we find a considerably higher average of annotations per object (7). 
We think that this might be an effect of our category selection procedure explained in Section \ref{sec:data}. However, interestingly, the portion of objects that have different names associated with them is still extremely small.
Note that in contrast, even though RefCOCO has much less annotations per object, there are many objects with different names (70\%).

@@

\subsection{Discussion}

While some existing resources do provide naming data for objects in context, they do not provide \textit{enough} data to systematically assess how variable or stable object naming really is. The RefCOCO data (and to some extent the Flickr30k entities data) suggests that for most objects there is more than none available name, but it is unclear which name most speakers would prefer or whether there is such a preferred name at all. 
The VG data, to the contrary, seems to indicate that the vast majority of objects should only be associated with a single name, but it is difficult to estimate to what extent this finding results from problems with annotation (partial linking).
This shows that to be able to analyze object naming in more detail, we simply need naming data from many subjects for the same objects. 
Also, dense annotations of images can be beneficial to analyze the factors affecting naming (e.g.,\ the category or salience of other objects), and how these impact the modeling of natural language in L\&V.
These are the motivations for our dataset, ManyNames, and for building it on top of \vg, as discussed next.
